---
title: "Alcohol vs Seat choice"
author: "Gabriela Lemus"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??
 
The data came from UCDavis in the year... 

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

# Methods 
In the data set davisdata Seat is a categorical variable, alcohol is numerical

we try to predict alcohol ~ seat so we use the.... helper file 

# Results 

## Descriptive Results 

### Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```


This box plot shows that there is a larger group that sit in the back who consume the alcohol rather than those in the front or middle seats.  

### Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


The numerical summary shows that the difference between the back seats and the seats in the middle and the front are more likely to consume alcohol. 

### Inferntial Results 
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


The P-value is 0.000116, less than 0.05 so we reject the null Hypothesis.
There is a difference in alcholo consumption based on where they sit. 

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```


## Conclusions

The interval in the middle-front contains a zero, showing that there is no statistical difference in the alcohol consumption by the people who occupy the seats middle-front.

The intervals in the front-back and middle-back show that there is a statistical difference between both because they do not contain a zero. 





